---
title: "Stats Modeling Overview"
author: "AG Schissler"
date: "1/22/2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Statistical modeling workflow

![Modeling workflow](stats_modeling_workflow.pdf)

## Quick example: Vapor pressure of mercury as a function of temperature

```{r pressure, echo=TRUE}
## 'pressure data set' is automatically loaded in 
## workspace through package{datasets}
head(pressure)
```

## Data set structure

```{r pres_str, echo = TRUE}
str(pressure)
```

## Numeric summary of pressure and temperature

```{r pres_sum, echo = TRUE}
summary(pressure)
```

## Visualization pressure and temperature relationalship

```{r pres_plot, echo = TRUE}
plot(pressure)
```

## Maybe pressure increases linearly with temperature?

- If that's true then a model could be: 
- pressure = b0 + b1*temperature
- Let's generate fake data and fit a linear model (simple linear regression!)

## Generate fake data from pressure = b0 + b1*temperature
```{r pres_fake, echo = TRUE,fig.height=4}
## pick values b0 and b1
b0 <- 0
b1 <- 10
## store in dataset as a new variable
fake_temp <- b0 + b1*pressure$temperature
plot(pressure$temperature, fake_temp)
```

## Fit a simple linear regression model
```{r pres_fake_lm, echo = TRUE}
fake_lm <- lm(formula = fake_temp ~ pressure$temperature)
summary(fake_lm)
```

## Hmm, model seems too perfect, add noise??
```{r pres_fake2, echo = TRUE,fig.height=4}
set.seed(44)
error <- rnorm(n = nrow(pressure), mean = 0, sd = 100)
fake_temp <- b0 + b1*pressure$temperature + error
plot(x = pressure$temperature, y = fake_temp)
```

## Fit a simple linear regression model with noise in data
```{r pres_fake_lm2, echo = TRUE}
fake_lm <- lm(formula = fake_temp ~ pressure$temperature)
summary(fake_lm)
```