---
title: "Stats Modeling Overview"
author: "AG Schissler"
date: "1/25/2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Statistical modeling workflow

![Modeling workflow](stats_modeling_workflow.pdf)

## Quick example: Stopping distance for speeding cars

```{r cars, echo=TRUE}
## 'pressure data set' is automatically loaded in 
## workspace through package{datasets}
head(cars)
```

## Data set structure

```{r cars_str, echo = TRUE}
str(cars)
```

## Numeric summary of pressure and temperature

```{r cars_sum, echo = TRUE}
summary(cars)
```

## Visualization of speed and dist relationship

```{r cars_plot, echo = TRUE}
plot(cars)
```

## Maybe stopping distance increases linearly with speed?

- If that's true then a model could be: 
- dist = b0 + b1*speed
- Let's generate fake data and fit a linear model (simple linear regression!)

## Generate fake data from pressure = b0 + b1*temperature
```{r cars_fake, echo = TRUE,fig.height=4}
## pick values b0 and b1
b0 <- 0
b1 <- 5
## store in dataset as a new variable
cars$fake_dist <- b0 + b1*cars$speed
plot(x = cars$speed, y = cars$fake_dist)
```

## Fit a simple linear regression model
```{r cars_fake_lm, echo = TRUE}
fake_lm <- lm(formula = fake_dist ~ speed, data = cars)
summary(fake_lm)
```

## Hmm, data seem too perfect, add noise??
```{r cars_fake2, echo = TRUE,fig.height=4}
set.seed(440)
error <- rnorm(n = nrow(cars), mean = 0, sd = 10)
cars$fake_dist <- b0 + b1*cars$speed + error
par(mfrow=c(1,2))
hist(error, breaks = 12)
plot(x = cars$speed, y = cars$fake_dist)
```

## Fit a simple linear regression model with noise in data
```{r pres_fake_lm2, echo = TRUE}
fake_lm <- lm(formula = fake_dist ~ speed, data = cars)
## attributes(fake_lm)
summary(fake_lm)
sd(fake_lm$residuals) ## naive estimate of error variance
```

## Plot the regression line
```{r cars_fake2_plot, echo = TRUE, fig.height=4}
plot(x = cars$speed, y = cars$fake_dist)
abline(fake_lm)
```

## Plot some diagnostics
```{r cars_fake2_resid_plot, echo = TRUE, fig.height=4}
par(mfrow=c(1,2))
plot(fake_lm)
```

## Fit model on real data
```{r cars_real, echo = TRUE}
real_lm <- lm(formula = dist ~ speed, data = cars)
summary(real_lm)
```

## Plot the regression line
```{r cars_real_plot, echo = TRUE, fig.height=4}
par(mfrow=c(1,1))
plot(x = cars$speed, y = cars$dist)
abline(real_lm)
```

## Plot some diagnostics
```{r cars_real_resid_plot, echo = TRUE, fig.height=4}
par(mfrow=c(1,2))
plot(real_lm)
```
